E Coli Project Paper Incredibly Rough Draft

### 2013-09-04 paper/paper.tex
very small paper change Tested everything on node26.

\fixme{should read following citation more carefully, worried -
  abstract says that simple models don't explain certain experimental
  findings.} \cite{ivanov2010multiple}

>>>>

\fixme{should read following citation more carefully, worried -
  abstract says that simple models don't explain certain experimental
  findings.} \cite{ivanov2010multiple} \fixme{should read following
  more carefully this is Huang doing much the same as what were doing}
\cite{varma2008min}
